\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
Conclusion

%------------------------------------------------
\section{Conclusions}
\label{concl}
%% TODO %%
% Draw conlusions from both the results and discussion
%%

>>>>

%------------------------------------------------
\section{Conclusions}
\label{concl}
The most obvious conclusion we draw from the worst-case complexity and computational results is that fast refinement is a faster algorithm than basic refinement. However, when we compare the computational results with their calculated worst-case complexity we observe some differences.

The complexity of basic refinement we determined is $O(N^3)$. When we look at the relative growth, it seems that the algorithm approaches $O(N^2)$. There could be two causes:
\begin{compactitem}
	\item The determined complexity of $O(N^3)$ was faulty.
	\item The type of graphs used, threegraphs, aproach a $O(N^2)$ complexity because of their structure. $O(N^3)$ was determined as worst-case.
\end{compactitem}

The complexity of fast refinement we determined is $O(MlogN)$. When we look at the relative growth, it seems that the algorithm approaches a linear complexity. We attribute this to the structure of the type of graphs used, threegraphs. $O(MlogN)$ was determined as worst-case.
%% TODO %%
% Draw conlusions from both the results and discussion
%%
